### 2023-09-14 cv/cv-body.tex
Update CV
Update bib
Add pubs

>>>>

Yalcin, S., \textbf{S.C. Anderson}, P.M. Regular, P.A. English.
Exploring the limits of spatiotemporal and design-based index
standardization under reduced survey coverage. In press at ICES Journal
of Marine Science.
K.L. Blake, D. Veríssimo, \textbf{S.C. Anderson}, A. Gleave. Do species
receive more attention when named after celebrities? In press at
Conservation Biology. Preprint:
\url{https://doi.org/10.31235/osf.io/wgbpv}.
J. Nephin, P.L. Thompson, \textbf{S.C. Anderson}, A.E. Park, C.N.
Rooper, B. Aulthouse, J. Watson. Integrating disparate survey data in
species distribution models demonstrates the need for robust model
evaluation. In press at Canadian Journal of Fisheries and Aquatic
Science.
Davies S.C., P.L. Thompson, C. Gomez, J. Nephin, A. Knudby, A.E. Park,
S.K. Friesen, L.J. Pollock, E.M. Rubidge, \textbf{S.C. Anderson}, J.C.
Iacarella, D.A. Lyons, A.A. MacDonald, A. McMillan, E.J. Ward, A.M.
Holdsworth, N. Swart, J. Price, K.L. Hunter. Addressing uncertainty when
projecting marine species' distributions under climate change.
Ecography: e06731. \url{https://doi.org/10.1111/ecog.06731}.
